% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\documentclass[11pt]{article}

	% ==========================================================================================
	% ==========================================================================================
	% ==========================================================================================

	% packages

	\usepackage{microtype}
	\frenchspacing
	\usepackage{xltxtra,comment,soul,titling}
	\usepackage[all]{nowidow}
	\usepackage[explicit]{titlesec}
	\usepackage[top=0.9in, bottom=0.9in, left=1.45in, right=1.45in]{geometry} 
	\usepackage[usenames,dvipsnames]{xcolor}

	% ==========================================================================================
	% ==========================================================================================
	% ==========================================================================================

	% global definitions

	\def\mycolor{myRed}%
	\definecolor{\mycolor}{RGB}{191,48,40}

	\setlength{\parindent}{0pt}
	\setlength{\parskip}{4pt}

	\setromanfont{Equity Text A}
	\setsansfont{Concourse T4}

	% ==========================================================================================
	% ==========================================================================================
	% ==========================================================================================

	% doc info

    \author{John Terhorst}
    \title{Curriculum Vit\ae}
    \def\position{Adjunct Assistant Professor of Chemistry}
    \def\currempl{Vanguard University of Southern California}

    \newif\ifweb
 	%\webfalse % 
 	\webtrue
 	\ifweb
 		\def\address{55 Fair Drive, Costa Mesa, California 92626}
	    \def\dept{Dept.\ of Environmental and Chemical Sciences}
	    \renewcommand{\maketitle}{
			{\vspace*{0.15cm}\huge{\color{\mycolor}\hspace*{1.0mm}\textbf{\theauthor}} / \hspace{-0.5mm}\thetitle}

			\position\ / \dept \\
			\currempl\ / \address

			\vspace*{0pt}
			}
	\else
	    \def\address{26 Kendall Avenue, Redlands, California 92373}
	    \def\phone{562.458.8254}
	    \def\mymail{\email{john@johnterhorst.com}}
	    \renewcommand{\maketitle}{
			{\vspace*{0.15cm}\huge{\color{\mycolor}\hspace*{1.0mm}\textbf{\theauthor}} / \hspace{-0.5mm}\thetitle}

			\position\ / \currempl \\
			\address\ / \phone\ / \mymail 

			\vspace*{0pt}
			}
	\fi
	
	\begin{comment}
	\renewcommand{\maketitle}{
			{\huge{\color{\mycolor}\textbf{\theauthor}} / \hspace{-0.5mm}\thetitle}
			\vspace*{12pt}
			}
	\end{comment}

	% ==========================================================================================
	% ==========================================================================================
	% ==========================================================================================

	% global formatting

	\titleformat{\section}
	{\normalfont}
	{}
	{0em}
	{\uppercase{\so{#1}} \hrulefill}
	\titlespacing\section{0pt}{8pt}{3pt}

	\titleformat{\subsection}
	{\normalfont\bfseries\itshape}
	{}
	{0em}
	{#1}
	\titlespacing\subsection{0pt}{8pt}{2pt}

	\newcommand{\doilink}[1]{\href{http://dx.doi.org/#1}{#1}} 

	\newcommand{\doi}[1]{doi:\doilink{#1}}

	\newcommand{\email}[1]{\href{mailto:#1}{#1}}

	\newcommand{\paritem}[2]{\textbf{#1} #2}

    \newcommand{\eduitem}[4]{\textbf{#1}, \textbf{#2}, #3\\#4}

    \newcommand{\careeritem}[4]{\textbf{#1}, #2\\#3, #4}

   	\newcommand{\teitem}[4]{\textbf{#1}: #2 #3 \textbf{#4}}

   	\newcommand{\lectitem}[2]{\textbf{#1} #2}

    \newcommand{\resitem}[7]{\textbf{#1}, \textbf{#2}, \textbf{#3}, #4\\#5 \textit{#6}: #7}

    \newcommand{\pubitem}[7]{{#1} {``#2''} \textit{#3} (#4), \textit{#5}, #6. \doi{#7}}

    \newcommand{\thesis}[7]{#1 #2 #3. #4. #5, #6. {#7 pages.}}

    \newcommand{\sciprog}[5]{#1. #2 (#3): #4 #5}          

    \newcommand{\pres}[8]{#1 #2. #3. #4, #5, #6. #7, #8.}

    \newcommand{\presnp}[8]{#1 #2 #3. #4, #5, #6. #7, #8.}

	% ==========================================================================================
	% ==========================================================================================
	% ==========================================================================================

	% metadata

	\usepackage{hyperref}
		\hypersetup{
		        colorlinks = false,
		        urlcolor = blue,
		        pdfauthor = {John Terhorst},
		        pdfkeywords = {chemistry, computational chemistry, organic chemistry, 
		                       drug design, continuum solvation, GB/SA, force fields, OPLS,
		                       professor, teacher, Yale, Redlands, Vanguard, university},
		        pdftitle = {John Terhorst: CV},
		        pdfsubject = {John Terhorst: CV},
		        pdfpagemode = UseNone}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\begin{document}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\maketitle

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Profile}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

I am a \textbf{college professor and private tutor} with 17 years of teaching experience. In these roles I teach college classes and \textbf{engage with students to help nurture a passion for and excitement about} science. 

\begin{comment}

\paritem{Research} {in Monte Carlo statistical perturbation theory for computing free-energy binding affinities using implicit solvent models, including software design and implementation.} 

\paritem{Development} {of molecular mechanics force fields including explicit treatment of polarization effects for use in computer-aided drug design of therapeutic agents targeting infectious, inflammatory, and hyperproliferative diseases.} 

\paritem{Seventeen years experience in instruction} {of chemistry, including organic chemistry and spectroscopy lecture and lab courses, as a teaching assistant, private tutor, graduate teaching fellow, and university professor.}

\end{comment}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Career Summary}

\careeritem{Adjunct Professor of Chemistry}{2020--Present}
{University of Redlands}{Redlands, California.}

\careeritem{Adjunct Assistant Professor of Chemistry}{2012--Present}
{Vanguard University}{Costa Mesa, California.}

\careeritem{Private Tutor}{2012--Present}
{WyzAnt, Inc.}{Redlands, California.}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Education}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\eduitem{Ph.D.\ in Chemistry}{\href{http://www.yale.edu/}{Yale University}}{2006--2011}
{Chemical theory and computation.} 

\eduitem{M.S.\ in Chemistry}{\href{http://www.yale.edu/}{Yale University}}{2006--2008}
{Physical organic chemistry.} 

\eduitem{B.S.\ in Chemistry}{\href{http://www.redlands.edu/}{University of Redlands}}{2002--2006}
{Departmental Honors.} 

\eduitem{B.S.\ in Biology}{\href{http://www.redlands.edu/}{University of Redlands}}{2002--2006}
{Biochemistry program.} 

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Teaching Experience}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\vspace*{-2mm} \smallskip {\small \textbf{P}, Professor / \textbf{F}, Teaching Fellow / \textbf{A}, Teaching Assistant / \textbf{T}, Tutor / \textbf{G}, Group Tutor} \vspace*{-2mm}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\subsection{WyzAnt Tutoring}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\teitem{Introductory, Honors, A.P., General, and Organic Chemistry}{Yale University, Stanford University, Dartmouth College, Tulane University, UNC Chapel Hill, Texas A\&M University, University of Miami, University of Delaware, Vanderbilt University, Boston University, University of Kentucky, Phillips Andover Academy, UC Irvine, UC Riverside, University of Southern California, University of Redlands, La Sierra University, Chapman University, Cal State Fullerton, Furman University, Saddleback College, Irvine Valley College, 
University High School, Newport Beach High School, Woodbridge High School, San Juan Hills High School, Corona del Mar High School, Yorba Linda High School, Mater Dei High School, Troy High School, Cornelia Connelly School, Sage Hill School, Deerfield Academy, Fairmont Preparatory Academy.}{1500+ hours, 2012--2021.}{T, G} 

\teitem{Public Profile}{\href{https://www.wyzant.com/match/tutor/80301850}{https://www.wyzant.com/match/tutor/80301850,}}{5.0$\star$ (400+ ratings)}{}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Teaching Experience (Cont.)}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\subsection*{Vanguard University of Southern California}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\teitem{CHEM 485}{Research Topics in Chemistry. Computational, theoretical, and physical organic chemistry.}{Summer 2013--2018.}{P}

%\teitem{CHEM 455}{Chemistry Teaching Internship. Oversight of students planning and conducting a lecture, recitation, and/or laboratory course.}{Fall and Spring 2016--2021}{P}

\teitem{CHEM 308}{Introduction to Spectroscopy. Includes IR spectroscopy, \raisebox{1mm}{\scriptsize 1}H and \raisebox{1mm}{\scriptsize 13}C NMR spectroscopy, mass spectrometry, and UV/vis spectrophotometry.}{Spring 2014.}{P}

\teitem{CHEM 304/305}{Organic Chemistry I/II. Functional groups, nomenclature, stereochemistry, aromaticity, reaction mechanisms, and molecular orbital theory.}{Summer 2012--2021, Fall 2019 and 2021, and Spring 2013, 2016, and 2021.}{P} 

\teitem{CHEM 120/121}{General Chemistry I/II. Atomic structure, bonding, stoichiometry, and reactions; kinetics, equilibrium, thermodynamics, and electrochemistry.}{Spring 2016--2021, and Fall 2015--2021.}{P}

\teitem{CHEM 113}{Fundamentals of General, Organic, and Biochemistry II. Functional groups, simple organic reactions, carbohydrates, lipids, proteins, nucleic acids, and biochemical applications.}{Spring 2013--2015.}{P} 

\teitem{CHEM 112C}{Fundamentals of General, Organic, and Biochemistry I. Atomic theory, periodic trends, measurements, stoichiometry, chemical reactions and equilibrium, and acids and bases.}{Fall 2013--2014.}{P}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\subsection{Yale University}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\teitem{CHEM 222/223}{Organic Chemistry Lab I/II. Reflux, TLC, recrystallization, column chromatography, extraction, Grignard chemistry, Williamson ether synthesis, aldol and Claisen condensations, and sodium borohydride reduction.}{Fall, 2006 and Spring, 2007.}{F}

\teitem{CHEM 221}{Organic Chemistry of Life Processes. A continuation of  Introductory Organic Chemistry, covering reactivity and mechanisms in organic chemistry with an emphasis in their various roles in biological processes.}{Fall, 2009 and Spring, 2010.}{T}

\teitem{CHEM 220}{Introductory Organic Chemistry. The first semester in a two-semester sequence offers a comprehensive look at the fundamental principles of organic chemistry. Offered off-sequence for students on an accelerated track.}{Spring, 2010.}{F, T}

\teitem{CHEM 114}{General Chemistry I. Descriptive, inorganic, and physical chemistry. Atomic theory, stoichiometry, thermochemistry, periodicity, bonding, and molecular geometry.}{Fall, 2007.}{F}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\subsection{University of Redlands}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\teitem{CHEM 231/232}{Organic Chemistry I/II. Comprehensive survey of the chemistry of carbon-containing compounds, their structure, nomenclature, physical properties, spectroscopy (IR, GC-MS, NMR), stereochemistry, chemical reactivities, reaction mechanisms, and synthesis.}{Fall, 2004 through Spring, 2006.}{T, G, A}

\teitem{CHEM 131/132}{General Chemistry I/II.  A two-semester sequence covering stoichiometry and modern views of the properties, structure, and reactivity of atoms and molecules.}{Fall, 2003 and 2020 and Spring, 2004 and 2021.}{P, T}

\teitem{CHEM 102}{Chemistry and the Environment. Introductory course for students wishing to explore the science or needing preparation for General Chemistry. Topics in chemistry relevant to the environment, such as energy needs, pollution, and pesticides.}{Fall, 2021.}{P}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\begin{comment}
\section{Invited Guest Lectures}

\lectitem{How Do You Know?}{University of Redlands Seminar. Department of Chemistry, University of Redlands, Redlands, California. January, 2020.}

\lectitem{Chemistry Through Computers.}{7th Grade Science Lecture. Blessed Sacrament Parish School, San Diego, California. January, 2015.}

\lectitem{Chemistry: College, Grad School, and Beyond.}{Guest Science Lecture. Citrus Valley High School, Redlands, California. May, 2012.}

\lectitem{Using Computers in Drug Discovery.}{University of Redlands Seminar. Department of Chemistry, University of Redlands, Redlands, California. January, 2011.}
\end{comment}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Honors, Awards, and Fellowships}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\eduitem{Dox Research Fellowship}{Yale University}{2009}
{The Dox Fellowship was established to provide stipend support to graduate students 
in the field of organic chemistry, given in recognition of excellence in academics and research.}

\eduitem{Distinguished Chemistry Fellowship}{Yale University}{2006--2011}
{Graduate students of exceptional promise are awarded the Distinguished Chemistry Fellowship for five years of
stipend support while conducting research towards the completion of a doctorate in chemistry.}

\eduitem{Graduate \textit{Summa cum Laude}}{University of Redlands}{2006}
{Latin honors of \textit{summa cum laude} are conferred upon graduating seniors who possess a cumulative 
GPA of 3.85 or higher.}

%\eduitem{Phi Beta Kappa}{Xi Chapter of Southern California}{2006}{Graduating seniors at the University of Redlands are inducted into PBK in recognition of excellence in the liberal arts and sciences.}

\eduitem{Robert D.\ Engel Award}{University of Redlands}{2006}
{The Robert D.\ Engel award is given to the outstanding senior 
science major at the University of Redlands.}

\eduitem{Edmund C.\ Jaeger Award}{University of Redlands}{2005}
{The Edmund C.\ Jaeger award is given by the University of Redlands for exceptional scholarship 
to a junior male biology student planning a career in teaching or research.}

%\eduitem{Tutor of the Year}{University of Redlands}{2005}
%{The title of Tutor of the Year is given in recognition of a tutor's valuable contributions to the University of Redlands' Tutoring Center.}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Research Experience}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\textbf{Director}, Summer Undergraduate Research Program, Vanguard University, 2015 

\resitem{Research Advisor}{Computational Chemistry}{Vanguard University}{2013--2016, 2018}
{Studies of pure liquids, conformational dynamics, and molecular design of anti-HIV agents.}
{Advisees}{Chris Bridges (B.S., 2014), Justin Pugh (B.S., 2014), Josiah Morales (B.S., 2014), Brennan Gregory (B.S., 2016), Chalane Records (B.S., 2015), Ashley Harris (B.S., 2016),  Israel Sanchez (B.S., 2016), Emily Eggleston (B.S., 2018), Mia Kilekas (B.S., 2018), and Kacie Qui\~nones, (B.S., 2019).}

\resitem{Graduate Student}{Chemical Theory and Computation}{Yale University}{2007--2011}
{Conformational dynamics, molecular mechanical 
force field parameters, and new methods for computing free 
energies of binding using continuum solvent models in a Monte Carlo 
manifold.}{Advisor}{William L.\ Jorgensen.}

\resitem{Undergraduate Student}{Organic Chemistry}{University of Redlands}{2004--2006}
{The [3+2] cycloaddition of carbonyl oxides in the synthesis of 1,2-dioxolanes, 
preparation of carbonyl oxides from precursors other than primary ozonides, 
and total synthesis of jasmine ketolactone.}{Advisor}{David P.\ Soulsby.}

\resitem{Undergraduate Student}{Theoretical Chemistry}{University of Redlands}{2003--2004}
{Theoretical investigations of photopumping in doubly illuminated liquid membranes containing photoactive carriers.}{Advisor}
{Teresa Longin.}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Publications}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\pubitem{\textbf{Terhorst, J}.; Jorgensen, W. L.}
{\textit{E}/\textit{Z} Energetics for Molecular Modeling and Design.}
{J.\ Chem.\ Theory Comput.}
{2010}{6}%{9}
{2762--2769}{10.1021/ct1004017}

\pubitem{Longin, T. L.; \textbf{Terhorst, J}.; Lang, C.}
{Simulations of Photopumping in Doubly Illuminated Liquid Membranes Containing Photoactive Carriers.}
{J.\ Phys.\ Chem.\ B}
{2010}{114}%{48}
{15846--15856}{10.1021/jp106802q}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Theses}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\thesis{\textbf{Terhorst, J}.}
{Continuum Solvent Models and Force Field Development in Computer-Aided Drug Design. ProQuest UMI-3496989.}
{Ph.D. Dissertation}{2011}{Yale University}{New Haven, Connecticut}{153} 

\thesis{\textbf{Terhorst, J}.}
{An Efficient Method for Calculating Born Energies with the GB/SA Solvation Model in Monte Carlo Simulations.}
{Thesis Prospectus}{2008}{Yale University}{New Haven, Connecticut}{14}

\thesis{\textbf{Terhorst, J}.}
{Theoretical Studies of Photopumping in Photofacilitated Liquid Membranes and The [3+2] Cycloaddition of Carbonyl Oxides in the Synthesis of 1,2-Dioxolanes.}
{Honors Thesis}{2006}{University of Redlands}{Redlands, California}{96}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Scientific Programming}

\sciprog{\href{http://zarbi.chem.yale.edu/software.html}{MCPRO}}
{Jorgensen, W. L.; Tirado-Rives, J.}
{contributor, proprietary}
{Implementation of new modules for utilizing the GB/SA continuum solvent 
model in simulations with Monte Carlo free-energy perturbation.}
{2008--2011}

\sciprog{\href{http://zarbi.chem.yale.edu/software.html}{BOSS}}
{Jorgensen, W. L.; Tirado-Rives, J.}
{contributor, proprietary}
{Development of new OPLS-AA parameters for 
functionalized heterocyles, and expansion of code for 
inclusion of solvent-by-solvent polarization within the 
OPLS-AA polarizable force field.}
{2008--2011}

\sciprog{DIHOPT}
{\textbf{Terhorst, J}.; Jorgensen, W. L.}
{chief author, open source}
{A Perl utility for automated discovery and optimization 
of dihedral torsion coefficients for the OPLS-AA force field.}
{2010}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Selected Presentations}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\presnp{\textbf{Terhorst, J}.}
{How Do You Know?}
{Chemistry Seminar}
{Department of Chemistry}
{University of Redlands}
{Redlands, California}
{January}{2020}

\pres{Eggleston, E.; Kilekas, M.; \textbf{Terhorst, J}.}
{Computer-Aided Drug Design Using Free-Energy Perturbation and Molecular Docking}
{SURP Symposium}
{Department of Chemistry}
{Vanguard University}
{Costa Mesa, California}
{June}{2016}

\pres{Pugh, J.; \textbf{Terhorst, J}.}
{Computer-Aided Drug Design Concerning HIV}
{Southern California Undergraduate Research Conference on Chemistry and Biochemistry}
{Department of Chemistry}
{Concordia University}
{Irvine, California}
{April}{2014}

\pres{\textbf{Terhorst, J}.; Jorgensen, W.\ L.}
{Optimizing the OPLS Force Field for NNRTI Drug Design}
{Bristol-Meyers Squibb Symposium}
{Department of Chemistry}
{Yale University}
{New Haven, Connecticut}
{August}{2011}

\begin{comment}
\pres{\textbf{Terhorst, J}.; Jorgensen, W.\ L.}
{Examining Intersubstituent Distances in Heterocycles and Evaluation of Tautomeric Equilibria}
{Connecticut Organic Chemistry Symposium}
{Northeast Region}
{American Chemical Society}
{New Haven, Connecticut}
{January}{2010}
\end{comment}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\section{Technical Skills}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\textbf{Laboratory Skills and Expertise:} Organic synthesis, separation (column chromatography, extraction, recrystallization, distillation), characterization (GC-MS, NMR, IR, UV/Vis), computational chemistry (MM, QM, MC, MC/FEP, GB/SA). \textbf{Chemical Simulation and Visualization:} BOSS, MCPRO, Gaussian, MGL AutoDock, Spartan, Chimera, PyMol. \textbf{Productivity:} Microsoft Office, vim, GNUplot. \textbf{Programming:} Perl, FORTRAN, HTML, bash/tcsh, \LaTeX, GNUprof. \textbf{Operating Systems:} macOS, Linux (Debian/Ubuntu), UNIX, Windows.

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\vspace*{5mm}\hfill\mbox{\textcolor{\mycolor}{\rule{5mm}{5mm}}}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================

\end{document}

% ==========================================================================================
% ==========================================================================================
% ==========================================================================================



